### 2016-12-01 paper/chapters/vae.tex
add relation to other AEs

>>>>

\paragraph{Relation to Auto-Encoders}
The Variational autoencoder has the same overall architecture than other autoencoders, for example sparse or denoising autoencoders.
Similar to other autoencoder frameworks VAE provides an encoder as well as a decoder model, but in contrast to other autoencoders both networks are probabilistic. This means that the model described by the VAE framework can be seen as a jointly trained probabilistic encoder and probabilistic decoder.
%One of the main differences is that the VAE framework enforces a specific prior distribution on the latent space, most of the time simply an isotropic gaussian.
